# Task 190146

We present the results of our analysis of `task 190146` with the different selection set splits used in our study.

```{r task-190146-data, echo=TRUE}
task_data <- filter(results, task_id == 190146)
```

## 5%

### Test accuracy

```{r task-190146-test-05-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '5%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-test-05-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '5%'))
```

The permutation test revealed that the results are:
```{r task-190146-test-05-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '5%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '5%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 41,
                    alternative = "g")
```

### Validation accuracy

```{r task-190146-select-05-perf, echo=TRUE, out.width="100%"}
validation_plot(filter(task_data, split == '5%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-select-05-sum, echo=TRUE, out.width="100%"}
validation_accuracy_summary(filter(task_data, split == '5%'))
```

The permutation test revealed that the results are:
```{r task-190146-select-05-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '5%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '5%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 42,
                    alternative = "l")
```


### Pipeline complexity

```{r task-190146-complexity-05-perf, echo=TRUE, out.width="100%"}
complexity_plot(filter(task_data, split == '5%'))
```

Summary statistics for the pipeline complexity of the selection schemes at the 5% selection set split:
```{r task-190146-complexity-05-sum, echo=TRUE, out.width="100%"}
complexity_summary(filter(task_data, split == '5%'))
```

The permutation test revealed that the results are:
```{r task-190146-complexity-05-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '5%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '5%' & selection == 'lexicase')
permutation_test(tournament_results$testing_complexity,
                    lexicase_results$testing_complexity,
                    seed = 215,
                    alternative = "t")
```

## 10%

### Test accuracy

```{r task-190146-test-10-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '10%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-test-10-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '10%'))
```

The permutation test revealed that the results are:
```{r task-190146-test-10-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '10%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '10%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 43,
                    alternative = "t")
```

### Validation accuracy

```{r task-190146-select-10-perf, echo=TRUE, out.width="100%"}
validation_plot(filter(task_data, split == '10%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-select-10-sum, echo=TRUE, out.width="100%"}
validation_accuracy_summary(filter(task_data, split == '10%'))
```

The permutation test revealed that the results are:
```{r task-190146-select-10-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '10%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '10%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 44,
                    alternative = "l")
```


### Pipeline complexity

```{r task-190146-complexity-10-perf, echo=TRUE, out.width="100%"}
complexity_plot(filter(task_data, split == '10%'))
```

Summary statistics for the pipeline complexity of the selection schemes at the 5% selection set split:
```{r task-190146-complexity-10-sum, echo=TRUE, out.width="100%"}
complexity_summary(filter(task_data, split == '10%'))
```

The permutation test revealed that the results are:
```{r task-190146-complexity-10-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '10%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '10%' & selection == 'lexicase')
permutation_test(tournament_results$testing_complexity,
                    lexicase_results$testing_complexity,
                    seed = 216,
                    alternative = "t")
```

## 50%

### Test accuracy

```{r task-190146-test-50-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '50%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-test-50-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '50%'))
```

The permutation test revealed that the results are:
```{r task-190146-test-50-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '50%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '50%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 45,
                    alternative = "t")
```

### Validation accuracy

```{r task-190146-select-50-perf, echo=TRUE, out.width="100%"}
validation_plot(filter(task_data, split == '50%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-select-50-sum, echo=TRUE, out.width="100%"}
validation_accuracy_summary(filter(task_data, split == '50%'))
```

The permutation test revealed that the results are:
```{r task-190146-select-50-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '50%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '50%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 46,
                    alternative = "l")
```

### Pipeline complexity

```{r task-190146-complexity-50-perf, echo=TRUE, out.width="100%"}
complexity_plot(filter(task_data, split == '50%'))
```

Summary statistics for the pipeline complexity of the selection schemes at the 5% selection set split:
```{r task-190146-complexity-50-sum, echo=TRUE, out.width="100%"}
complexity_summary(filter(task_data, split == '50%'))
```

The permutation test revealed that the results are:
```{r task-190146-complexity-50-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '50%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '50%' & selection == 'lexicase')
permutation_test(tournament_results$testing_complexity,
                    lexicase_results$testing_complexity,
                    seed = 217,
                    alternative = "t")
```

## 90%

### Test accuracy

```{r task-190146-test-90-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '90%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-test-90-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '90%'))
```

The permutation test revealed that the results are:
```{r task-190146-test-90-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '90%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '90%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 47,
                    alternative = "t")
```

### Validation accuracy

```{r task-190146-select-90-perf, echo=TRUE, out.width="100%"}
validation_plot(filter(task_data, split == '90%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-select-90-sum, echo=TRUE, out.width="100%"}
validation_accuracy_summary(filter(task_data, split == '90%'))
```

The permutation test revealed that the results are:
```{r task-190146-select-90-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '90%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '90%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 48,
                    alternative = "l")
```


### Pipeline complexity

```{r task-190146-complexity-90-perf, echo=TRUE, out.width="100%"}
complexity_plot(filter(task_data, split == '90%'))
```

Summary statistics for the pipeline complexity of the selection schemes at the 5% selection set split:
```{r task-190146-complexity-90-sum, echo=TRUE, out.width="100%"}
complexity_summary(filter(task_data, split == '90%'))
```

The permutation test revealed that the results are:
```{r task-190146-complexity-90-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '90%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '90%' & selection == 'lexicase')
permutation_test(tournament_results$testing_complexity,
                    lexicase_results$testing_complexity,
                    seed = 218,
                    alternative = "t")
```

## 95%

### Test accuracy

```{r task-190146-test-95-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '95%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-test-95-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '95%'))
```

The permutation test revealed that the results are:
```{r task-190146-test-95-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '95%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '95%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 49,
                    alternative = "t")
```

### Validation accuracy

```{r task-190146-select-95-perf, echo=TRUE, out.width="100%"}
validation_plot(filter(task_data, split == '95%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-190146-select-95-sum, echo=TRUE, out.width="100%"}
validation_accuracy_summary(filter(task_data, split == '95%'))
```

The permutation test revealed that the results are:
```{r task-190146-select-95-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '95%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '95%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 50,
                    alternative = "l")
```

### Pipeline complexity

```{r task-190146-complexity-95-perf, echo=TRUE, out.width="100%"}
complexity_plot(filter(task_data, split == '95%'))
```

Summary statistics for the pipeline complexity of the selection schemes at the 5% selection set split:
```{r task-190146-complexity-95-sum, echo=TRUE, out.width="100%"}
complexity_summary(filter(task_data, split == '95%'))
```

The permutation test revealed that the results are:
```{r task-190146-complexity-95-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '95%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '95%' & selection == 'lexicase')
permutation_test(tournament_results$testing_complexity,
                    lexicase_results$testing_complexity,
                    seed = 219,
                    alternative = "t")
```