# Task 359958

We present the results of our analysis of `task 359958` with the different selection set splits used in our study.

```{r task-359958-data, echo=TRUE}
task_data <- filter(results, task_id == 359958)
```

## 5%

### Testing set accuracy

```{r task-359958-test-05-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '5%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-test-05-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '5%'))
```

The permutation test revealed that the results are:
```{r task-359958-test-05-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '5%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '5%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 71,
                    alternative = "t")
```

### Selection set accuracy

```{r task-359958-select-05-perf, echo=TRUE, out.width="100%"}
selection_plot(filter(task_data, split == '5%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-select-05-sum, echo=TRUE, out.width="100%"}
selection_results_summary(filter(task_data, split == '5%'))
```

The permutation test revealed that the results are:
```{r task-359958-select-05-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '5%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '5%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 72,
                    alternative = "l")
```

## 10%

### Testing set accuracy

```{r task-359958-test-10-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '10%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-test-10-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '10%'))
```

The permutation test revealed that the results are:
```{r task-359958-test-10-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '10%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '10%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 73,
                    alternative = "g")
```

### Selection set accuracy

```{r task-359958-select-10-perf, echo=TRUE, out.width="100%"}
selection_plot(filter(task_data, split == '10%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-select-10-sum, echo=TRUE, out.width="100%"}
selection_results_summary(filter(task_data, split == '10%'))
```

The permutation test revealed that the results are:
```{r task-359958-select-10-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '10%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '10%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 74,
                    alternative = "l")
```

## 50%

### Testing set accuracy

```{r task-359958-test-50-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '50%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-test-50-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '50%'))
```

The permutation test revealed that the results are:
```{r task-359958-test-50-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '50%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '50%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 75,
                    alternative = "t")
```

### Selection set accuracy

```{r task-359958-select-50-perf, echo=TRUE, out.width="100%"}
selection_plot(filter(task_data, split == '50%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-select-50-sum, echo=TRUE, out.width="100%"}
selection_results_summary(filter(task_data, split == '50%'))
```

The permutation test revealed that the results are:
```{r task-359958-select-50-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '50%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '50%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 76,
                    alternative = "l")
```

## 90%

### Testing set accuracy

```{r task-359958-test-90-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '90%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-test-90-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '90%'))
```

The permutation test revealed that the results are:
```{r task-359958-test-90-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '90%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '90%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 77,
                    alternative = "t")
```

### Selection set accuracy

```{r task-359958-select-90-perf, echo=TRUE, out.width="100%"}
selection_plot(filter(task_data, split == '90%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-select-90-sum, echo=TRUE, out.width="100%"}
selection_results_summary(filter(task_data, split == '90%'))
```

The permutation test revealed that the results are:
```{r task-359958-select-90-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '90%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '90%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 78,
                    alternative = "l")
```

## 95%

### Testing set accuracy

```{r task-359958-test-95-perf, echo=TRUE, out.width="100%"}
test_plot(filter(task_data, split == '95%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-test-95-sum, echo=TRUE, out.width="100%"}
test_results_summary(filter(task_data, split == '95%'))
```

The permutation test revealed that the results are:
```{r task-359958-test-95-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '95%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '95%' & selection == 'lexicase')
permutation_test(tournament_results$testing_performance,
                    lexicase_results$testing_performance,
                    seed = 79,
                    alternative = "t")
```

### Selection set accuracy

```{r task-359958-select-95-perf, echo=TRUE, out.width="100%"}
selection_plot(filter(task_data, split == '95%'))
```

Summary statistics for the testing performance of the selection schemes at the 5% selection set split:
```{r task-359958-select-95-sum, echo=TRUE, out.width="100%"}
selection_results_summary(filter(task_data, split == '95%'))
```

The permutation test revealed that the results are:
```{r task-359958-select-95-pv, echo=TRUE, out.width="100%"}
tournament_results <- filter(task_data, split == '95%' & selection == 'tournament')
lexicase_results <- filter(task_data, split == '95%' & selection == 'lexicase')
permutation_test(tournament_results$training_performance,
                    lexicase_results$training_performance,
                    seed = 80,
                    alternative = "l")
```